%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Benjamin}{Carothers}{ \urlstyle{same}\url{http://carothers.io} \\
\href{mailto:ben@carothers.io}{ben@carothers.io} | (941)-928-8020
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.25\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Education}

\subsection{New College}
\subsection{of Florida}
\descript{BA in Computer Science}
\location{Expected May 2017 | Sarasota, FL}
\sectionsep


\subsection{Thesis}
\descript{Victor: Building Monitored, Secured, and Self-Sustaining IOT Hydroponic Gardens}
\location{Expected May 2017}
\sectionsep

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Technology
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Languages}
\descript{Proficient}
Python,  JavaScript,  Node,  HTML,  CSS,  SQL \\
\descript{Experience}
C, Java, PHP, Mongo, Bash
\sectionsep

\section{Frameworks}
\descript{Web}
Angular, Express, Serverless, Passport, Bootstrap \\

\sectionsep
\section{Tools}
Nmap, Shodan, Burp, Unix, Docker, SwaggerIO
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}
USCC CTF Winner\\
AFFIRM Security Summit Invitee\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Volunteering
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Volunteering}
Hour of Code Initiative \\
US Cyber Challenge \\
Ocean Technology Club\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/btcrs}{\custombold{btcrs}} \\
LinkedIn://  \href{https://www.linkedin.com/in/btcrs}{\custombold{btcrs}} \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.70\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Mote Marine Laboratory}
\descript{| Ocean Technology Teacher}
\location{February 2017 - Present | Sarasota, FL}
\vspace{\topsep}
\begin{tightemize}
\item Sourced components to build a field datalogger based on the Arduino platform.
\item Created a build log and developed a curriculum to help teach high school students how microprocessors operate, embedded programming, and low-level communication. 
\end{tightemize}
\sectionsep

\runsubsection{Cyber Ninjas}
\descript{| Cyber Security Intern}
\location{January 2016 - Present | Sarasota, FL}
\begin{tightemize}
\item Play a significant role in red team engagements. Handle information gathering, exploitation of relevant, high-impact vulnerabilities, and reporting of findings.
\item Create single-page, self-contained web applications to teach current topics in cyber security including XSS, SQL Injection, and Session Fixation.
\end{tightemize}
\sectionsep

\runsubsection{Mote Marine Laboratory}
\descript{| Software Engineering Intern}
\location{January 2016 - January 2017 | Sarasota, FL}
\begin{tightemize}
\item Created a Python library and scripting engine to control the BB4 Optical Phytoplankton Discriminator.
\item Oversaw IOT security to secure both the administration application and BB4 devices.
\end{tightemize}
\sectionsep

\runsubsection{Star2star}
\descript{| Software Engineering Intern}
\location{October 2015 - December 2015 | Sarasota, FL}
\begin{tightemize}
\item Created a work flow for providing partners with requested reports using IPython scripts to interface with CPQ and construct canned reports locked down by ACLs
\item Altered the quote generation business logic to reduce the number of switches included and sent to any given location by as much as 50 percent.
\end{tightemize}
\sectionsep

\runsubsection{Intensive Air Ambulance}
\descript{| Web Developer}
\location{Jan 2011 – May 2013 | Sarasota, FL}
\begin{tightemize}
\item Maintained quoting software written in PHP that was integral to day-to-day function and touched 70 percent of all revenue generating operations.
\item Developed a suite of tools to programmatically generate contracts.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Porter}
\descript{| Reporting Engine}
\location{Jan 2016 – Present}
A framework for interfacing with common penetration testing tools to automate the process of reporting findings. Used Python and a DOCX templating engine to bootstrap long term engagement reports by using Metasploit's SQL database, CSV output from Nessus, and flat file input.
\sectionsep

\runsubsection{Buckets}
\descript{| Judging NBA lineups by floor coverage}
\location{Aug 2016 – Dec 2016}
Constructed the strongest offensive five man lineups using current (2015 - 2016) starting NBA players. Using the NBA player's data API I wrote a Node program that gathered every attempted shot taken during the 2015-2016 season, determined each players shooting average for 12 spatial zones of the scoring area, and tried to pair players that occupied most of the court with strong shooting.
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}
